%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Omar Roldan
% Based on a template by  Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}  


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} 
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Qiang Han}}}} % First name
	
	\vspace{6pt}
	
	{\Large Software Development Engineer} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% \icon{Globe}{11}{\href{http://www.google.com}{portafolio.com}}\\ 
    \icon{Phone}{11}{+86 13811001112}\\
    % \icon{MapMarker}{11}{City, Country}\\
    \icon{LinkedinSquare}{11}{\href{https://www.linkedin.com/in/qiang-han}{/in/qiang-han}}\\    

\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\icon{Envelope}{11}{\href{mailto:qiang.han@hotmail.com}{qiang.han@hotmail.com}}\\	
    \icon{Github}{11}{\href{https://github.com/qiang-han}{github.com/qiang-han}}\\
    
\end{minipage}


%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.46\textwidth}
    \cvsect{Summary}
	\vspace{-6pt}
 
    {Experienced Software Development Engineer with a Master's degree in Communication Information Engineering. Specializes in camera imaging, multimedia, and cloud networking software development.}
    {Successfully led project development, practiced Agile methodologies as a Scrum Master, and drove innovation in complex technical environments.}

\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.465\textwidth}
    \cvsect{Skills}
    \vspace{-6pt}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Languages:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
      C, C++, Bash, Python
    \end{minipage}
    \vspace{4mm}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Technologies:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
      Linux, Docker, Kubernetes, Camera \& Imaging, Media Transportation, Networking
    \end{minipage}
\end{minipage}

\vspace{10pt}

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\cvsect{Projects}
\begin{entrylist}
    \entry
        {Technical \newline Leader}
		{Media Communications Mesh}
		{https://github.com/OpenVisualCloud/Media-Communications-Mesh}
        {Led the development of an efficient, low-latency, and high-throughput media transport service mesh framework, optimizing for microservices architectures. Collaborated with architects to fine-tune design and led project development and management, ensuring milestones were met. Implemented key features such as zero-copy transportation, SMPTE 2110 standards, NMOS integration, and Kubernetes orchestration.}
    \entry
        {Technical \newline Leader}
		{E2E Media Pipeline}
		{}
		{Led the development of the "E2E Media Pipeline" program, delivering a benchmarking tool to develop a reference media pipeline for Intel platforms.
        Developed key features using the FFmpeg "libav" library, including performance and quality benchmarking, parallel running model, and high configurability.
        Instrumental in analyzing media performance on existing and next-gen "Xeon" platforms.}
	\entry
        {Technical \newline Leader}
		{Camera Automated Test Suit}
		{}
        {Designed and developed a comprehensive automated test framework for Intel's high-end camera and imaging systems.
        Fully automated the complete workflow of camera validation tasks, encompassing case management, test execution, automatic result analysis, bug auto-submission, and test report generation.}
    \entry
		{Technical \newline Leader}
		{IPU System Test Automation}
		{}
        {Designed and implemented an automated testing framework for Intel's Image Processing Unit (IPU) system,
        achieving and maintaining automation rate over 90\% across 2,000+ test cases.
        Developed innovative automated solutions for critical IPU tests, such as ATE bit-match, static analysis (Klocwork/Protex/BDBA),
        and compliance testing, substantially increasing test efficiency and reliability.}
    \entry
		{Project \newline Management}
		{Validation Project Leader}
		{}
        {
        Served as the Validation Project Leader for various Intel IPU projects, managing the full validation
        process from requirements analysis to test case development.
        Expertly coordinated project schedules and resource allocation, formulated comprehensive test
        plans, and ensured the timely progression of both development and validation phases.
        Employed 'Agile' methodologies as a Scrum Master, host regular scrum meetings and was a key contributor to the scrum team.
        }
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Education}
\begin{entrylist}
    \entry
		{9/2004 - 3/2007}
		{Master of Science in Engineering}
		{Beihang University}
		{Specialty: Communication Information Engineering}
    \entry
		{9/1996 - 7/2000}
		{Bachelor of Engineering}
		{Tianjin Polytechnic University}
		{Specialty: Computer Science and Application}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Experience}
\begin{entrylist}
	\entry
        {11/2021 -- Present}
		{System Software Development Engineer, NEX (Network \& Edge Group)}
		{Intel Corporation}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Develop software about multi-media, video codec, and cloud networking.
            Optimize software design and implementation to achieve the maximum performance on Xeon platforms.
        \end{itemize} 
        \texttt{C} \slashsep \texttt{C++} \slashsep \texttt{Service Mesh} \slashsep \texttt{Kubernetes} \slashsep \texttt{SMPTE 2110}  \slashsep \texttt{NMOS} \slashsep \texttt{FFmpeg}}
	\entry
		{2/2011 -- 11/2021}
		{Senior Software Engineer, ICG (Imaging and Camera Technologies Group)}
		{Intel Corporation}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Engaged in software development and validation for “Camera \& Imaging” system, including design and develop test framework and test tools, test automation, validation project management etc.
        \end{itemize} 
        \texttt{C} \slashsep \texttt{Python} \slashsep \texttt{Gtk+} \slashsep \texttt{OpenCV} \slashsep \texttt{Android} \slashsep \texttt{Agile}}
	\entry
		{4/2009 -- 11/2009}
		{Software Engineer}
		{Lenovo Corporate Research \& Development}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item SMS client, OSD components on “Skylight” mobile device.
        \end{itemize} 
        \texttt{Linux} \slashsep \texttt{C} \slashsep \texttt{Gtk+} \slashsep \texttt{OpenEmbedded}}
	\entry
		{5/2007 -- 4/2009}
		{Software Engineer}
		{Beijing Peking University Unity Microsystems Technology Co., Ltd.}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Network computer (NC) Terminals and the Servers management system
            \item Digital photo frame application
        \end{itemize} 
        \texttt{Linux} \slashsep \texttt{C} \slashsep \texttt{Gtk+}}
	\entry
		{5/2004 -- 3/2007 \\\footnotesize{Internship}}
		{Software Engineer}
		{China Aviation Data Communication Corp (ADCC)}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Data Link Gateway Server System for CAAC
            \item The Surveillance System of the Flight for the Airline
        \end{itemize}
        \texttt{Linux} \slashsep \texttt{C} \slashsep \texttt{Gtk+} \slashsep \texttt{SNMP} \slashsep \texttt{Oracle9i} \slashsep \texttt{MS VC++} \slashsep \texttt{DirectX}}
	\entry
		{7/2000 -- 6/2002}
		{Software Engineer}
		{COSCO Bulk Carrier CO., LTD.}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item ERP system for company daily business management
        \end{itemize}
        \texttt{ASP} \slashsep \texttt{JavaScript} \slashsep \texttt{VBScript} \slashsep \texttt{IBM DB2} \slashsep \texttt{SQL Server 2000}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	Innovation
%----------------------------------------------------------------------------------------
\cvsect{Innovation}
\begin{itemize}
\vspace{-10pt}
    \item E2E Media Pipeline for Platform Performance Evaluation \& Optimization - SWPC, 2022
    \item Automated SWQRC Report in ICG Dashboard System - SWPC, 2019
    \item Hybrid Camera Simulation Solution for Pre-Silicon Development - DTTC, 2017
    \item Intellectual Test Case Selection Strategy - SWPC, 2017
    \item Smart Light Booth Based on Intel Edison - I2R, 2016
    \item Deploy Test Management System using Intel Internal Cloud Service - SWPC, 2016
    \item Network Management System Based on AgentX Extensible Network Management Model - Application Research of Computers, 2006
\end{itemize}

\vspace{10pt}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
	\cvsect{Languages}
    \vspace{-6pt}
    
    \hspace{26mm} \textbf{English} - proficient, \textbf{Chinese} - native

%----------------------------------------------------------------------------------------

\end{document}
